Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-09-01 semiring.tex
corrected review typos

%\medskip
\noindent
We need to extend ~$\oplus to infinitely many operands$.
A semiring~$\Semiring$ is called \emph{complete}~\cite{Droste09handbook}
%(\cite{Droste09handbook} chapter 1) %\cite{Kuich97semirings}
if it has an %infinite sum
operation $\bigoplus_{i \in I} x_i$
for every family
$(x_i)_{i \in I}$ %$\{ x_i \mid i \in I \}$
of elements of $\dom(\Semiring)$ over an index set $I \subseteq \mathbb{N}$, such that:
\begin{description}
\item[$i.$]
\emph{infinite sums extend finite sums:}\\
$\displaystyle\bigoplus_{i \in \emptyset} x_i = \zero$,\quad
      $\forall j\in \mathbb{N}, \displaystyle\bigoplus_{i \in \{ j \}} x_i = x_j$,
      $\forall j, k\in \mathbb{N}, j\neq k,
      \displaystyle\bigoplus_{i \in \{ j, k \}} x_i = x_j \oplus x_k$,
%
\item[$ii.$]
\emph{associativity and commutativity:}\\
for evert $I \subseteq \mathbb{N}$
and all partition $(I_{j})_{j \in J}$ of $I$, %\subseteq \mathbb{N}$,
\(
\displaystyle
\bigoplus_{j \in J}\bigoplus_{i \in I_j} x_i =
\bigoplus_{i \in I} x_i
\),
%
\item[$iii.$]
\emph{distributivity of product over infinite sum:}\\
for every $I \subseteq \mathbb{N}$,
\(
\displaystyle
\bigoplus_{i \in I} (x \otimes y_i) = x \otimes \bigoplus_{i\in I} y_i\), and
\(
\displaystyle
\bigoplus_{i \in I} (x_i \otimes y) = (\bigoplus_{i \in I} x_i ) \otimes y\).
\end{description}

>>>>

%\medskip
\noindent
We need to extend ~$\oplus to infinitely many operands$.
A semiring~$\Semiring$ is called \emph{complete}~\cite{Droste09handbook}
%(\cite{Droste09handbook} chapter 1) %\cite{Kuich97semirings}
if it has an %infinite sum
operation $\bigoplus_{i \in I} x_i$
for every family
$(x_i)_{i \in I}$ %$\{ x_i \mid i \in I \}$
of elements of $\dom(\Semiring)$ over an index set $I \subseteq \mathbb{N}$, such that:
\begin{description}
\item[$i.$]
\emph{infinite sums extend finite sums:}\\
$\displaystyle\bigoplus_{i \in \emptyset} x_i = \zero$,\quad
      $\forall j\in \mathbb{N}, \displaystyle\bigoplus_{i \in \{ j \}} x_i = x_j$,
      $\forall j, k\in \mathbb{N}, j\neq k,
      \displaystyle\bigoplus_{i \in \{ j, k \}} x_i = x_j \oplus x_k$,
%
\item[$ii.$]
\emph{associativity and commutativity:}\\
for evert $I \subseteq \mathbb{N}$
and all partitions $(I_{j})_{j \in J}$ of $I$, %\subseteq \mathbb{N}$,
\(
\displaystyle
\bigoplus_{j \in J}\bigoplus_{i \in I_j} x_i =
\bigoplus_{i \in I} x_i
\),
%
\item[$iii.$]
\emph{distributivity of products over infinite sums:}\\
for every $I \subseteq \mathbb{N}$,
\(
\displaystyle
\bigoplus_{i \in I} (x \otimes y_i) = x \otimes \bigoplus_{i\in I} y_i\), and
\(
\displaystyle
\bigoplus_{i \in I} (x_i \otimes y) = (\bigoplus_{i \in I} x_i ) \otimes y\).
\end{description}
